Lab 12: Covariate Balancing and CBPS: Answers

### 2023-04-12 Lab 14  RDD/Lab12_covariatebalance_Answers.Rmd
Add files via upload

---
title: 'Lab 13: Covariate Balancing and CBPS: Answers'
author: "Eric Parajon with code adapted from Colin Case"
output:
  pdf_document: default
  html_document: default
header-include:
- \usepackage{amsbsy}
- \usepackage{amsmath}
- \usepackage{amssymb}
- \DeclareMathOperator*{\argmin}{argmin} % thin space, limits underneath in displays
---

@@

stargazer(tmod1, tmod2, tmod3, type="html",
          covariate.labels = c("Primed",
                               "Political Interest",
                               "Female",
                               "Østlandet",
                               "Sørlandet",
                               "Vestlandet",
                               "Trøndelag",
                               "Nord-Norge",
                               "Completed Upper Secondary Education",
                               "Completed University/ College Education",
                               "Born between 1940-1949",
                               "Born between 1950-1959",
                               "Born between 1960-1969",
                               "Born between 1970-1979",
                               "Born between 1980-1989",
                               "Born in or after 1990",
                               "Intercept"),
          se=list(NULL, NULL, corr_se),
          column.labels = c("No Weights OLS", "PS Weights SWLS", "PS/NCP Weights SWLS"),
          star.cutoffs = c(.10,.05,.01,.001),
          star.char = c("+","*","**","***"),
          column.sep.width = "10pt",
          notes = c("p<.10+, p<.05*, p<.01**, p<.001***"),
          single.row = TRUE,
          notes.append=FALSE)
```

From the three models reported, we see that there is a small positive effect of being primed the cost of the existing municipal structure. Across three models, the effect is significant, p<.10+. These primed respondents are likely to increase their rating of the conservative party .1 point more on a 1-7 scale. The effect size is modest but it is statistically significant in all three models, regardless of the weighting method used.

>>>>

---
title: 'Lab 12: Covariate Balancing and CBPS: Answers'
author: "Eric Parajon with code adapted from Colin Case"
output:
  html_document: default
  pdf_document: default
header-include:
- \usepackage{amsbsy}
- \usepackage{amsmath}
- \usepackage{amssymb}
- \DeclareMathOperator*{\argmin}{argmin} % thin space, limits underneath in displays
---

@@

stargazer(tmod1, tmod2, tmod3, type="html",
          covariate.labels = c("Primed",
                               "Political Interest",
                               "Female",
                               "Østlandet",
                               "Sørlandet",
                               "Vestlandet",
                               "Trøndelag",
                               "Nord-Norge",
                               "Completed Upper Secondary Education",
                               "Completed University/ College Education",
                               "Born between 1940-1949",
                               "Born between 1950-1959",
                               "Born between 1960-1969",
                               "Born between 1970-1979",
                               "Born between 1980-1989",
                               "Born in or after 1990",
                               "Intercept"),
          se=list(NULL, NULL, corr_se),
          column.labels = c("No Weights", "PS Weights", "PS/NCP Weights"),
          star.cutoffs = c(.10,.05,.01,.001),
          star.char = c("+","*","**","***"),
          column.sep.width = "11pt",
          notes = c("p<.10+, p<.05*, p<.01**, p<.001***"),
          single.row = TRUE,
          notes.append=FALSE)
```

**Interpretation**: From the three models reported, we see that there is a small positive effect of being primed the cost of the existing municipal structure. Across three models, the effect is significant, p<.10+. These primed respondents are likely to increase their rating of the conservative party .1 point more on a 1-7 scale. The effect size is modest but it is statistically significant in all three models, regardless of the weighting method used.
